Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
added more commented comments and inline comments

% LL: David, thanks for polishing up the related work!
%LL: Related work put at the end upon David's Suggestion. Paper flow is much better. 
\section{Related Work}
In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.

>>>>

% LL: David, thanks for polishing up the related work!
%LL: Related work put at the end upon David's Suggestion. Paper flow is much better. 
\section{Related Work}
{\color{red} this section is still rough! David will redo.} In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.
